Formalizing Stack Safety as a Security Property

### 2021-10-02 submission4/main.tex
Referenced artifact and fixed figure numbers

We find that Roessler and DeHon's {\em Depth Isolation} micro-policy, in
which memory within each stack frame is tagged with the depth of
the function activation that owns the frame and access is
permitted only when an activation at that depth is currently executing, validates our
stepwise properties. On the other hand, our testing reveals that \emph{Lazy Tagging and Clearing}
violates the temporal aspect of confidentiality in
corner cases where data can leak across repeated calls to the same callee,
and also violates integrity if the leak happens to use the caller's frame. We
propose a variant of {\em Lazy Tagging and Clearing} that testably enforces
confidentiality, albeit at some performance cost.
%
\ifaftersubmission
\bcp{Did Nick and Andre know about this deficiency?  Did they mention
  it in their paper?  (If neither, we should make a bigger deal out of the
  fact that we discovered it.)\apt{Their paper is a little vague on this subject.
    They refer to ``temporal security properties'' as something to do with dangling
    pointers, but they don't define it.
    Then they say that Depth Isolation has weaker temporal security
    guarantees than Static Authorities (tag=function name), but they don't explain why
    (and I don't see why). They don't say anything explicit about the temporal
    security properties of Lazy Tagging and Clearing, but they consider it to enforce
    a completely different (and generally weaker) policy anyway (``data flow
    integrity'' vs. ``memory safety'').}}\bcp{Sigh.  OK, I propose that we
  leave this issue to deal with later (in consultation with them, which we
  don't have time to do a good job of today).  At any rate, by my reading we
are not saying anything incorrect at the moment.}
\fi

@@

\begin{itemize}
\item We adapt concepts of integrity and confidentiality from language-based
security and combine these with an existing notion of well-bracketed
control flow to formalize a {\em stepwise stack safety}
property that captures the intuitive concept of
strict stack safety enforced over each step of execution~(\cref{sec:prelim,sec:lse}).
As a case study, we explore how our properties are enforced
by the {\em Depth Isolation} micro-policy
of Roessler and DeHon\cite{DBLP:conf/sp/RoesslerD18}, but not by some of its optimized variants~(\cref{sec:enforcement}).
\item We formalize weaker but more extensional \emph{observational} variants of
  confidentiality and integrity. Both are parameterized over a notion of external
  observation, and are violated only if accessing secrets or overwriting
  data causes a visible change in the system behavior (\cref{sec:lazy}).
\item We show that our definitions can be
extended to describe argument passing on the stack, callee-saves registers, exceptions, and a simple coroutine system (\cref{sec:ext}).
\item We use property-based random testing to validate the relationship between
  our properties and micro-policies (\cref{sec:testing})
\end{itemize}
\Cref{sec:relwork,sec:future} discuss related and future work.
\apt{Say something about the Coq artifact?}

@@

\begin{figure}
\begin{subfigure}{.4\columnwidth}
  {\small
\begin{lstlisting}
int main() {
  int x;
  x = f();
  return g();
}
int f() {
  int y = 5;
  return y;
}
int g() {
  int z;
  return z;
}
\end{lstlisting}
  }
\vspace*{-1em}
\caption{Leaking via uninitialized data}
\vspace*{-1em}
\label{fig:conf2}
\end{subfigure}
\begin{subfigure}{.5\columnwidth}
  \begin{center}
\begin{tabular}{l l}
2 &
\memoryaddrs{8em}
\memory{3}{\unsealc}[\unsealdesc]

~$\cdots$
\vspace{.5em}
\\
3 &
\memoryaddrs{8em}
\memory{3}{\unsealc}
~$\cdots$
    \MemoryLabel{-15em}{0.75em}{42}
    \vspace{.5em}
\\
12 &
\memoryaddrs{16em}
\memory{1}{\mainsealc}[\sealdesc{0}]%
\memory{1}{\retptrc}[\retptrdesc]%
\memory{1}{\unsealc}[\unsealdesc]
~$\cdots$
\MemoryLabel{-16em}{0.75em}{42}
\MemoryLabel{-7.5em}{0.75em}{42}
\vspace{.5em}
\\
13 &
\memoryaddrs{16em}
\memory{1}{\mainsealc}
\memory{1}{\retptrc}
\memory{1}{\unsealc}
~$\cdots$
\MemoryLabel{-15em}{0.75em}{\bf 0}
\vspace{.5em}
\end{tabular}
\end{center}
\caption{Integrity Violation Trace}
\label{fig:int1}
\end{subfigure}
\vspace*{1em}
\caption{}
\end{figure}

>>>>

We find that Roessler and DeHon's {\em Depth Isolation} micro-policy, in
which memory within each stack frame is tagged with the depth of
the function activation that owns the frame and access is
permitted only when an activation at that depth is currently executing, validates our
stepwise properties. On the other hand, our testing reveals that \emph{Lazy Tagging and Clearing}
violates the temporal aspect of confidentiality in
cases where data can leak across repeated calls to the same callee,
and also violates integrity if the leak uses the caller's frame. We
propose a variant of {\em Lazy Tagging and Clearing} that testably enforces
confidentiality, albeit at some performance cost.
%
\ifaftersubmission
\bcp{Did Nick and Andre know about this deficiency?  Did they mention
  it in their paper?  (If neither, we should make a bigger deal out of the
  fact that we discovered it.)\apt{Their paper is a little vague on this subject.
    They refer to ``temporal security properties'' as something to do with dangling
    pointers, but they don't define it.
    Then they say that Depth Isolation has weaker temporal security
    guarantees than Static Authorities (tag=function name), but they don't explain why
    (and I don't see why). They don't say anything explicit about the temporal
    security properties of Lazy Tagging and Clearing, but they consider it to enforce
    a completely different (and generally weaker) policy anyway (``data flow
    integrity'' vs. ``memory safety'').}}\bcp{Sigh.  OK, I propose that we
  leave this issue to deal with later (in consultation with them, which we
  don't have time to do a good job of today).  At any rate, by my reading we
are not saying anything incorrect at the moment.}
\fi

@@

\begin{itemize}
\item We adapt concepts of integrity and confidentiality from language-based
security and combine these with an existing notion of well-bracketed
control flow to formalize a {\em stepwise stack safety}
property that captures the intuitive concept of
strict stack safety enforced over each step of execution~(\cref{sec:prelim,sec:lse}).
As a case study, we explore how our properties are enforced
by the {\em Depth Isolation} micro-policy
of Roessler and DeHon\cite{DBLP:conf/sp/RoesslerD18}, but not by some of its optimized variants~(\cref{sec:enforcement}).
\item We formalize weaker but more extensional \emph{observational} variants of
  confidentiality and integrity. Both are parameterized over a notion of external
  observation, and are violated only if accessing secrets or overwriting
  data causes a visible change in the system behavior (\cref{sec:lazy}).
\item We show that our definitions can be
extended to describe argument passing on the stack, callee-saves registers, exceptions, and a simple coroutine system (\cref{sec:ext}).
\item We use property-based random testing to validate the relationship between
  our properties and micro-policies (\cref{sec:testing})
\end{itemize}
\Cref{sec:relwork,sec:future} discuss related and future work.

Our artifact contains Coq formalizations of our properties for illustrative purposes
as well as the testing implementation.

@@

\begin{figure}
\begin{subfigure}{.4\columnwidth}
  {\small
\begin{lstlisting}
int main() {
  int x;
  x = f();
  return g();
}
int f() {
  int y = 5;
  return y;
}
int g() {
  int z;
  return z;
}
\end{lstlisting}
  }
\vspace*{-1em}
\caption*{Fig. \arabic{figure}: Leaking via\\ uninitialized data}
\addtocounter{figure}{1}
\vspace*{-1em}
\label{fig:conf2}
\end{subfigure}
\begin{subfigure}{.5\columnwidth}
  \begin{center}
\begin{tabular}{l l}
2 &
\memoryaddrs{8em}
\memory{3}{\unsealc}[\unsealdesc]

~$\cdots$
\vspace{.5em}
\\
3 &
\memoryaddrs{8em}
\memory{3}{\unsealc}
~$\cdots$
    \MemoryLabel{-15em}{0.75em}{42}
    \vspace{.5em}
\\
12 &
\memoryaddrs{16em}
\memory{1}{\mainsealc}[\sealdesc{0}]%
\memory{1}{\retptrc}[\retptrdesc]%
\memory{1}{\unsealc}[\unsealdesc]
~$\cdots$
\MemoryLabel{-16em}{0.75em}{42}
\MemoryLabel{-7.5em}{0.75em}{42}
\vspace{.5em}
\\
13 &
\memoryaddrs{16em}
\memory{1}{\mainsealc}
\memory{1}{\retptrc}
\memory{1}{\unsealc}
~$\cdots$
\MemoryLabel{-15em}{0.75em}{\bf 0}
\vspace{.5em}
\end{tabular}
\end{center}
\caption*{Fig. \arabic{figure}: Integrity Violation Trace}
\label{fig:int1}
\end{subfigure}
\vspace*{1em}
\vspace*{-2em}
\end{figure}
